 

### 2023-03-02 appendix_2.2.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

data_mh <- rbind(csb_data, chd_data, chu_data) %>% # Join all data
  select(commune, district, region, clinic_name) %>%
  mutate(region = str_to_title(region), # Capitalizing region names
         clinic_name = str_squish(clinic_name)) %>%
  unique()

@@

n_facilities_name <- data_mh %>% select(clinic_name) %>% unique %>% nrow()
n_facilities <- data_mh %>% unique %>% nrow()

@@

data_mh_dup_names <- data_mh %>%
  select(region, clinic_name) %>% unique()

@@

# data_mh_dup_names %>%
#   select(region, clinic_name) %>%
#   unique() %>%
#   filter(clinic_name %in% duplicates) %>%
#   relocate(clinic_name, .before = region) %>%
#   arrange(clinic_name) %>%
#   group_by(clinic_name) %>%
#   summarise(region = paste(region, collapse = " | ")) %>%
#   unique() %>%
#   rename("Facility name" = clinic_name,
#          "Regions" = region) %>%
#   gt() %>% 
#   tab_header(
#     title = md("**Examples of duplicate facility names in different regions**")) %>%
#   tab_options(table.font.names = "Source Sans Pro") %>%
#   tab_style(
#     locations = cells_column_labels(),
#     style     = list(
#       cell_text(weight = "bold"))
#   )

@@

column2 <- data_mh %>% select(commune, district, region) %>% unique()
column1 <- facilities_all %>% select(region_name, district_name, commune_name) %>% unique()

r_old <- column1 %>% select(region_name) %>% unique()
r_new <- column2 %>% select(region) %>% unique()

cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
  filter(test == FALSE) %>%
  relocate(region, .before = region_name) %>%
  rename("Name in data" = region,
         "Standardized name" = region_name) %>%
  select(!test) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.6: Standardization of region names**"))

@@

as.data.frame(cbind(commune_old, commune_new)) %>%
  arrange(commune_old) %>%
  mutate(test = commune_new == commune_old) %>%
  filter(test == FALSE) %>%
  select(!test) %>%
  rename("Name in data" = commune_old,
         "Standardized name" = commune_new) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.9: Standardization of commune names**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )

@@

gps_source_join_map <- function(data){
  map_mdg_3 %>%
  st_transform(., crs = 4326) %>% 
  st_join(data,., join = st_within) %>%
  select(clinic_name, clinic_type, source, 
         COMMUNE_NA, DISTRICT_N, REGION_NAM, geometry) %>%
  rename(commune_name = COMMUNE_NA, 
         district_name = DISTRICT_N,
         region_name = REGION_NAM) %>%
      clean_clinic_name() %>%
      clean_catchment_area() %>%
      gps_source_match_prep() %>%
    filter(!is.na(commune_name) & !is.na(district_name) & !is.na(region_name))

@@

      # And drop all columns except for the unique commune-district-region name, centroid, and area
      select(area_km, full_name, geometry)

@@

  data_no_gps <- data_trim %>%
    select(full_name, facility_ID) %>%
    mutate(full_name = str_squish(full_name))

@@

    print("Matching on centroid")
    data_gps <- data_trim_2 %>%
    select(full_name, area_km) %>%
    mutate(full_name = str_squish(full_name))
    } else(
  data_gps <- data_trim_2 %>%
    select(full_name, ID) %>%
    mutate(full_name = str_squish(full_name))
    )

  ## We can save on run time by using innerjoin to match facilities where a match is identical
  perfect_matches <- inner_join(data_gps, data_no_gps)
in_perfect_matches <- perfect_matches %>% select(facility_ID) %>% unique()
  in_perfect_matches <- as.vector(in_perfect_matches$facility_ID)
  data_no_gps <- data_no_gps %>%    
    filter(!facility_ID %in% in_perfect_matches)

@@

 asm_matches <- match.nogps.gps %>%
    rename(full_name = s2name) %>%
    inner_join(., data_gps) %>%
    rename(full_name_gps = full_name,
           full_name = s1name)  %>%
    inner_join(., data_no_gps) %>%
    select(!c(s2.i, s1.i)) %>%
   rbind(perfect_matches) %>%
       arrange(adist)

@@

  asm_match %>%
    sample_frac(sample_fraction) %>% 
    st_drop_geometry %>%
    arrange(adist) %>%
    select(full_name, full_name_gps, adist) %>%
    rename("String (sample)" = full_name,
           "String (coord.)"= full_name_gps,
           "Levenshtein distance" = adist) %>%
    gt() %>%
    tab_header(
    title = md(paste0("Step ",
                            gsub("step_", "", step),
                            ": Approximate string matches"))) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )
}

@@

  facilities_all_gps_temp <- asm_matches_retained %>%
    select(geometry, facility_ID) %>%
    unique()

@@

  with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
  with_gps <- as.vector(with_gps$facility_ID)

@@

  facilities_all_gps_temp <- asm_matches_retained %>%
    filter(area_km <= ifelse(gps_source == "commune", commune_lim, fokontany_lim)) %>%
    st_sf() %>% 
    st_transform(crs = 4326) %>%
    select(geometry, facility_ID) %>%
    unique()

@@

         # "Health Centre" corresponds to CSB2
         clinic_type = gsub("Health Centre", "CSB2", clinic_type)) %>%
  select(!c(Country, Ownership)) %>%
    rename(source = LL.source,
         latitude = Lat,
         longitude = Long)

@@

facilities_gps_who_0 <- facilities_gps_who %>%
  select(clinic_type, latitude, longitude, source, clinic_name) %>%
  st_drop_geometry()

@@

facilities_gps_3 <- read.csv(paste(data_gps_sources_reposit,
                                   'MDMFL.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(longitude = Longitude, latitude = Latitude, 
         district_name = CommuneNom,
         clinic_name = FacilityNom, 
         clinic_type = FacilityType) %>%
  select(district_name, clinic_name, 
         clinic_type, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "RHINoVision Decision Support System") %>%
  select(clinic_name, longitude, latitude, source, clinic_type)

@@

facilities_gps_OCHA_1 <- st_read(paste(data_gps_sources_reposit, 
                                       "OCHA",
                                       "hotosm_mdg_health_facilities_points_shp",
                                       "hotosm_mdg_health_facilities_points.shp",
                                       sep = "/")) %>%
  select(name, geometry, osm_id) %>%
  unique() %>%
  filter(!is.na(name)) %>%
  rename(clinic_name = name, ID_OSM = osm_id)

@@

facilities_gps_OCHA_1 <- facilities_gps_OCHA_1 %>%
  st_drop_geometry() %>%
  select(clinic_name, X, Y, ID_OSM)

crs_system <- st_crs(facilities_gps_OCHA_1)
with_gps_OCHA <- facilities_gps_OCHA_1 %>% select(ID_OSM) %>% unique()
with_gps_OCHA <- with_gps_OCHA$ID_OSM

@@

facilities_gps_OCHA_2 <- read_csv(paste(data_gps_sources_reposit, 
                                        "OCHA",
                                        "madagascar.csv", 
                                        sep = "/")) %>%
  filter(!is.na(X)) %>%
  filter(!is.na(Y)) %>%
  filter(!is.na(name)) %>%
  select(name, X, Y, osm_id) %>%
  rename(clinic_name = name, ID_OSM = osm_id) %>%
  unique() %>%
  filter(!ID_OSM %in% with_gps_OCHA) %>%
  st_drop_geometry()

@@

# Import first source of data: OpenStreetMap data
facilities_gps_0 <- facilities_gps_OCHA %>%
  rename(latitude = Y,
         longitude = X) %>%
  mutate(source = "OpenStreetMap", type = NA) %>%
  select(!c(ID_OSM))

@@

  # Trim dataset
  select(region, district, commune, type, FS, longitude, latitude) %>%
  rename(clinic_name = FS, district_name = commune) %>%

  # Drop missing values
  filter(!is.na(longitude)) %>%
  filter(!is.na(latitude)) %>%
  mutate(source = "File 1 (Consultant?)") %>%
  select(clinic_name, longitude, latitude, source, type)

@@

  # Ensure longitude is saved as numeric, not character 
  mutate(longitude = as.numeric(longitude)) %>%
  select(Nom.Commune, Type..CSB1..CSB2.., 
         Nom.complet.FS.1, latitude, longitude) %>% 
  rename(clinic_name = Nom.complet.FS.1, 
         district_name = Nom.Commune, type = Type..CSB1..CSB2..) %>%
  unique() %>%
  mutate(source = "File 2 (MOH?)") %>%
  select(clinic_name, longitude, latitude, source, type) %>%

@@

# Import next source of GPS data
facilities_gps_4 <- read.csv(paste(data_gps_sources_reposit, 
                                   '20210415 Palu_CSB_last 3.csv',
                                   sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = District, clinic_name = Health.center.names) %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 3 (?)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

facilities_gps_5 <- read_excel(paste(data_gps_sources_reposit, 
                                     "CHD ET CHU XY 2012.xls", sep = "/")) %>%
  rename(district_name = "Nom District", 
         clinic_name = "Nom FS GESIS",
         latitude = "Y", longitude = "X") %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 4 (Consultant)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

# Import next source of GPS data
facilities_gps_6 <- read.csv(paste(data_gps_sources_reposit, 
                                   'CSB GPS points.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = district_n, clinic_name = clinic_nam,
         latitude = Latitude, longitude = Longitude) %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 5 (Chris)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

@@

facility_gps_types <- facilities_gps_any %>%
  st_drop_geometry() %>%
  mutate(count = 1) %>%
  group_by(source, clinic_type) %>%
  mutate(value = sum(count, na.rm = FALSE)) %>%
  ungroup() %>%
  select(source, clinic_type, value) %>%
  unique() %>%
  arrange(source) %>%
  pivot_wider(names_from = source) %>%
  arrange(clinic_type)

@@

n_mean_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  select(area_km) %>%
  mutate(mean = mean(area_km)) %>%
  select(mean) %>%
  unique()

@@

n_max_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  select(area_km) %>%
  mutate(max = max(area_km)) %>%
  select(max) %>%
  unique()
n_max_area_polygons <- n_max_area_polygons$max

n_mean_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  select(length) %>%
  mutate(mean = mean(length)) %>%
  select(mean) %>%
  unique()

@@

n_max_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  select(length) %>%
  mutate(max = max(length)) %>%
  select(max) %>%
  unique()
n_max_length <- n_max_length$max

@@

facilities_gps_any <- facilities_gps_any %>% 
  filter(retain == "Within threshold") %>%
  st_centroid() %>% 
  select(!c(shape_type, length, area_km, retain)) %>%
  clean_catchment_area() %>%
  unique() %>%
  gps_source_match_prep()

@@

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, clinic_name_new)) %>%

@@

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, clinic_type, clinic_type_new)) %>%

@@

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, district_name, district_name_new)) %>%

@@

  select(clinic_name, length) %>%
  arrange(length)

>>>>

data_mh <- rbind(csb_data, chd_data, chu_data) %>% # Join all data
  dplyr::select(commune, district, region, clinic_name) %>%
  mutate(region = str_to_title(region), # Capitalizing region names
         clinic_name = str_squish(clinic_name)) %>%
  unique()

@@

n_facilities_name <- data_mh %>% dplyr::select(clinic_name) %>% unique %>% nrow()
n_facilities <- data_mh %>% unique %>% nrow()

@@

data_mh_dup_names <- data_mh %>%
  dplyr::select(region, clinic_name) %>% unique()

@@

# data_mh_dup_names %>%
#   dplyr::select(region, clinic_name) %>%
#   unique() %>%
#   filter(clinic_name %in% duplicates) %>%
#   relocate(clinic_name, .before = region) %>%
#   arrange(clinic_name) %>%
#   group_by(clinic_name) %>%
#   summarise(region = paste(region, collapse = " | ")) %>%
#   unique() %>%
#   rename("Facility name" = clinic_name,
#          "Regions" = region) %>%
#   gt() %>% 
#   tab_header(
#     title = md("**Examples of duplicate facility names in different regions**")) %>%
#   tab_options(table.font.names = "Source Sans Pro") %>%
#   tab_style(
#     locations = cells_column_labels(),
#     style     = list(
#       cell_text(weight = "bold"))
#   )

@@

column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique()
column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()

r_old <- column1 %>% dplyr::select(region_name) %>% unique()
r_new <- column2 %>% dplyr::select(region) %>% unique()

cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
  filter(test == FALSE) %>%
  relocate(region, .before = region_name) %>%
  rename("Name in data" = region,
         "Standardized name" = region_name) %>%
  dplyr::select(!test) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.6: Standardization of region names**"))

@@

as.data.frame(cbind(commune_old, commune_new)) %>%
  arrange(commune_old) %>%
  mutate(test = commune_new == commune_old) %>%
  filter(test == FALSE) %>%
  dplyr::select(!test) %>%
  rename("Name in data" = commune_old,
         "Standardized name" = commune_new) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.9: Standardization of commune names**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )

@@

gps_source_join_map <- function(data){
  map_mdg_3 %>%
  st_transform(., crs = 4326) %>% 
  st_join(data,., join = st_within) %>%
  dplyr::select(clinic_name, clinic_type, source, 
         COMMUNE_NA, DISTRICT_N, REGION_NAM, geometry) %>%
  rename(commune_name = COMMUNE_NA, 
         district_name = DISTRICT_N,
         region_name = REGION_NAM) %>%
      clean_clinic_name() %>%
      clean_catchment_area() %>%
      gps_source_match_prep() %>%
    filter(!is.na(commune_name) & !is.na(district_name) & !is.na(region_name))

@@

      # And drop all columns except for the unique commune-district-region name, centroid, and area
      dplyr::select(area_km, full_name, geometry)

@@

  data_no_gps <- data_trim %>%
    dplyr::select(full_name, facility_ID) %>%
    mutate(full_name = str_squish(full_name))

@@

    print("Matching on centroid")
    data_gps <- data_trim_2 %>%
    dplyr::select(full_name, area_km) %>%
    mutate(full_name = str_squish(full_name))
    } else(
  data_gps <- data_trim_2 %>%
    dplyr::select(full_name, ID) %>%
    mutate(full_name = str_squish(full_name))
    )

  ## We can save on run time by using innerjoin to match facilities where a match is identical
  perfect_matches <- inner_join(data_gps, data_no_gps)
in_perfect_matches <- perfect_matches %>% dplyr::select(facility_ID) %>% unique()
  in_perfect_matches <- as.vector(in_perfect_matches$facility_ID)
  data_no_gps <- data_no_gps %>%    
    filter(!facility_ID %in% in_perfect_matches)

@@

 asm_matches <- match.nogps.gps %>%
    rename(full_name = s2name) %>%
    inner_join(., data_gps) %>%
    rename(full_name_gps = full_name,
           full_name = s1name)  %>%
    inner_join(., data_no_gps) %>%
    dplyr::select(!c(s2.i, s1.i)) %>%
   rbind(perfect_matches) %>%
       arrange(adist)

@@

  asm_match %>%
    sample_frac(sample_fraction) %>% 
    st_drop_geometry %>%
    arrange(adist) %>%
    dplyr::select(full_name, full_name_gps, adist) %>%
    rename("String (sample)" = full_name,
           "String (coord.)"= full_name_gps,
           "Levenshtein distance" = adist) %>%
    gt() %>%
    tab_header(
    title = md(paste0("Step ",
                            gsub("step_", "", step),
                            ": Approximate string matches"))) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )
}

@@

  facilities_all_gps_temp <- asm_matches_retained %>%
    dplyr::select(geometry, facility_ID) %>%
    unique()

@@

  with_gps <- facilities_all_gps %>% dplyr::select(facility_ID) %>% unique()
  with_gps <- as.vector(with_gps$facility_ID)

@@

  facilities_all_gps_temp <- asm_matches_retained %>%
    filter(area_km <= ifelse(gps_source == "commune", commune_lim, fokontany_lim)) %>%
    st_sf() %>% 
    st_transform(crs = 4326) %>%
    dplyr::select(geometry, facility_ID) %>%
    unique()

@@

         # "Health Centre" corresponds to CSB2
         clinic_type = gsub("Health Centre", "CSB2", clinic_type)) %>%
  dplyr::select(!c(Country, Ownership)) %>%
    rename(source = LL.source,
         latitude = Lat,
         longitude = Long)

@@

facilities_gps_who_0 <- facilities_gps_who %>%
  dplyr::select(clinic_type, latitude, longitude, source, clinic_name) %>%
  st_drop_geometry()

@@

facilities_gps_3 <- read.csv(paste(data_gps_sources_reposit,
                                   'MDMFL.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(longitude = Longitude, latitude = Latitude, 
         district_name = CommuneNom,
         clinic_name = FacilityNom, 
         clinic_type = FacilityType) %>%
  dplyr::select(district_name, clinic_name, 
         clinic_type, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "RHINoVision Decision Support System") %>%
  dplyr::select(clinic_name, longitude, latitude, source, clinic_type)

@@

facilities_gps_OCHA_1 <- st_read(paste(data_gps_sources_reposit, 
                                       "OCHA",
                                       "hotosm_mdg_health_facilities_points_shp",
                                       "hotosm_mdg_health_facilities_points.shp",
                                       sep = "/")) %>%
  dplyr::select(name, geometry, osm_id) %>%
  unique() %>%
  filter(!is.na(name)) %>%
  rename(clinic_name = name, ID_OSM = osm_id)

@@

facilities_gps_OCHA_1 <- facilities_gps_OCHA_1 %>%
  st_drop_geometry() %>%
  dplyr::select(clinic_name, X, Y, ID_OSM)

crs_system <- st_crs(facilities_gps_OCHA_1)
with_gps_OCHA <- facilities_gps_OCHA_1 %>% dplyr::select(ID_OSM) %>% unique()
with_gps_OCHA <- with_gps_OCHA$ID_OSM

@@

facilities_gps_OCHA_2 <- read_csv(paste(data_gps_sources_reposit, 
                                        "OCHA",
                                        "madagascar.csv", 
                                        sep = "/")) %>%
  filter(!is.na(X)) %>%
  filter(!is.na(Y)) %>%
  filter(!is.na(name)) %>%
  dplyr::select(name, X, Y, osm_id) %>%
  rename(clinic_name = name, ID_OSM = osm_id) %>%
  unique() %>%
  filter(!ID_OSM %in% with_gps_OCHA) %>%
  st_drop_geometry()

@@

# Import first source of data: OpenStreetMap data
facilities_gps_0 <- facilities_gps_OCHA %>%
  rename(latitude = Y,
         longitude = X) %>%
  mutate(source = "OpenStreetMap", type = NA) %>%
  dplyr::select(!c(ID_OSM))

@@

  # Trim dataset
  dplyr::select(region, district, commune, type, FS, longitude, latitude) %>%
  rename(clinic_name = FS, district_name = commune) %>%

  # Drop missing values
  filter(!is.na(longitude)) %>%
  filter(!is.na(latitude)) %>%
  mutate(source = "File 1 (Consultant?)") %>%
  dplyr::select(clinic_name, longitude, latitude, source, type)

@@

  # Ensure longitude is saved as numeric, not character 
  mutate(longitude = as.numeric(longitude)) %>%
  dplyr::select(Nom.Commune, Type..CSB1..CSB2.., 
         Nom.complet.FS.1, latitude, longitude) %>% 
  rename(clinic_name = Nom.complet.FS.1, 
         district_name = Nom.Commune, type = Type..CSB1..CSB2..) %>%
  unique() %>%
  mutate(source = "File 2 (MOH?)") %>%
  dplyr::select(clinic_name, longitude, latitude, source, type) %>%

@@

# Import next source of GPS data
facilities_gps_4 <- read.csv(paste(data_gps_sources_reposit, 
                                   '20210415 Palu_CSB_last 3.csv',
                                   sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = District, clinic_name = Health.center.names) %>%
  dplyr::select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 3 (?)", type = NA) %>%
  dplyr::select(clinic_name, longitude, latitude, source, type)

facilities_gps_5 <- read_excel(paste(data_gps_sources_reposit, 
                                     "CHD ET CHU XY 2012.xls", sep = "/")) %>%
  rename(district_name = "Nom District", 
         clinic_name = "Nom FS GESIS",
         latitude = "Y", longitude = "X") %>%
  dplyr::select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 4 (Consultant)", type = NA) %>%
  dplyr::select(clinic_name, longitude, latitude, source, type)

# Import next source of GPS data
facilities_gps_6 <- read.csv(paste(data_gps_sources_reposit, 
                                   'CSB GPS points.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = district_n, clinic_name = clinic_nam,
         latitude = Latitude, longitude = Longitude) %>%
  dplyr::select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 5 (Chris)", type = NA) %>%
  dplyr::select(clinic_name, longitude, latitude, source, type)

@@

facility_gps_types <- facilities_gps_any %>%
  st_drop_geometry() %>%
  mutate(count = 1) %>%
  group_by(source, clinic_type) %>%
  mutate(value = sum(count, na.rm = FALSE)) %>%
  ungroup() %>%
  dplyr::select(source, clinic_type, value) %>%
  unique() %>%
  arrange(source) %>%
  pivot_wider(names_from = source) %>%
  arrange(clinic_type)

@@

n_mean_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  dplyr::select(area_km) %>%
  mutate(mean = mean(area_km)) %>%
  dplyr::select(mean) %>%
  unique()

@@

n_max_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  dplyr::select(area_km) %>%
  mutate(max = max(area_km)) %>%
  dplyr::select(max) %>%
  unique()
n_max_area_polygons <- n_max_area_polygons$max

n_mean_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  dplyr::select(length) %>%
  mutate(mean = mean(length)) %>%
  dplyr::select(mean) %>%
  unique()

@@

n_max_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  dplyr::select(length) %>%
  mutate(max = max(length)) %>%
  dplyr::select(max) %>%
  unique()
n_max_length <- n_max_length$max

@@

facilities_gps_any <- facilities_gps_any %>% 
  filter(retain == "Within threshold") %>%
  st_centroid() %>% 
  dplyr::select(!c(shape_type, length, area_km, retain)) %>%
  clean_catchment_area() %>%
  unique() %>%
  gps_source_match_prep()

@@

  facilities_manual_matches %>%
  dplyr::select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
dplyr::select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # dplyr::select(!c(region_name, region_name_new)) %>%
      dplyr::select(c(clinic_name, clinic_name_new)) %>%

@@

  facilities_manual_matches %>%
  dplyr::select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
dplyr::select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # dplyr::select(!c(region_name, region_name_new)) %>%
      dplyr::select(c(clinic_name, clinic_type, clinic_type_new)) %>%

@@

  facilities_manual_matches %>%
  dplyr::select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
dplyr::select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # dplyr::select(!c(region_name, region_name_new)) %>%
      dplyr::select(c(clinic_name, district_name, district_name_new)) %>%

@@

  dplyr::select(clinic_name, length) %>%
  arrange(length)
